---
output:
  pdf_document:
    latex_engine: xelatex
    keep_tex: yes
    fig_width: 7
    fig_height: 5
    fig_caption: yes
    extra_dependencies:
      flafter: []

header-includes:
  - \usepackage{graphicx}
  - \usepackage{placeins}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{caption}
  - \usepackage{subcaption}
  - \usepackage[linguistics,edges]{forest}
  - \usepackage{adjustbox}
  - \usepackage[labelformat = empty]{caption}
  
fontsize: 11pt
geometry: margin=0.5in

params:
  build_dir: "/Users/hailey/repos/psc/paper_reports/saps//performance_saps_yg_rf_K05N01_error_validation_onehot_impute_knn_onehot_sequential_gen"
  report_data: "/Users/hailey/repos/avni_debug/results/iris.results"
  report_python_dir: "/Users/hailey/repos/psc/"
  # build_dir: "/Users/berk/Dropbox (Harvard University)/repos/psc/reports/cshock4_yg_logreg_onehot_K05N01_error_validation_t0"
  # report_data: "/Users/berk/Dropbox (Harvard University)/repos/psc/results/cshock4_yg_logreg_onehot_K05N01_error_validation_t0.results"
  # report_python_dir: "/Users/berk/Dropbox (Harvard University)/repos/psc/"
  venv_dir: '/usr/local/anaconda3/envs/py37intel/' #python environment
---
---

```{r setup-r, include = FALSE}

# Use this chunk to default options for how to evaluate each code chunk in the template
# For a complete list of options, see: https://yihui.org/knitr/options/#package_options
knitr::opts_knit$set(
  echo = FALSE, # set to TRUE to print code in the final report?
  fig.path = 'figure/' # pass the path for where to store PDFs
  )
# Setting "echo = FALSE" here means that the template will not show the code in each chunk (by default)
# We can override this behavior for a specific chunk by adding "echo = TRUE" to the top of the chunk

# load R packages
packages = c('reticulate', 'tidyverse', 'xtable', 'stringr')
for (pkg in packages) {
  library(pkg, character.only = TRUE, warn.conflicts = FALSE, quietly = TRUE, verbose = FALSE)
}

# load reticulate virtual environment
# load python virtual environment for reticulate
tryCatch({
  use_condaenv(condaenv = params$venv_dir, required = TRUE)
}, error = function(error_condition) {
  use_virtualenv(virtualenv = params$venv_dir, required = TRUE)
})

```

```{python setup-python, include = FALSE}
# Use this chunk to set up your Python environment

import os
import sys
print(os.getcwd())

sys.path.append(r.params['report_python_dir'])

import dill
import numpy as np
import itertools
import pandas as pd
import matplotlib.pyplot as plt
from pathlib import Path
from datetime import datetime

```

```{=latex}
% Use this chunk to define Tex functions and run Tex commands
% Whatever you put here will be placed after "\begin{document}" so you can't import packages
% To import Tex packages just list them after `extra_dependencies`

\newcommand{\cell}[2]{\begin{tabular}{#1}#2\end{tabular}}
\pagenumbering{gobble}
```

```{python, include = FALSE}

# load the report data from Python
try:

  with open(r.params['report_data'], 'rb') as infile:
      results = dill.load(infile)

except ValueError:
  
  import pickle5 as pickle
  with open(r.params['report_data'], 'rb') as infile:
      results = pickle.load(infile)

```

This report is produced using the template `pyrmd/templates/demo_report.Rmd`. After running `usage.py`, open `demo_report.Rmd` document in RStudio to see how to write a template. The template file includes lots of content that is not shown in the PDF.

# Quick Introduction to RMarkdown

The template is composed of text and code chunks.

## Code Chunk Syntax

Code chunks are used to execute code in the template. R Markdown lets you write code chunks in R, Python, SQL, Latex. For example, we can use a chunk like this one:

```{python}
with open(r.params['report_data'], 'rb') as infile:
    results = dill.load(infile)
```

Code chunks can access variables from previous chunks. For example, the next Python code chunk can access `results`:

```{python}
assert(isinstance(results, dict))
```

Using `reticulate`, we can also access Python variables in an R code chunk via the `py` object.
```{r}

# access `results` as a list in R
py$results

# set foo to py$results$data_name
foo <- py$results$data_name

# set df to py$results$df
df <- py$results$df
```

Reticulate uses a straightforward mapping between different data types in Python and R:

- Python dict $\leftrightarrow$  R list
- Pandas DataFrame $\leftrightarrow$ R data.frame


## Text Syntax

Text is everything in a template that is not included in a code chunk. This text is parsed as `R Markdown syntax`, which is basic Markdown with some Latex mixed in. For a quick overview, check out [this quick introduction](https://www.stat.cmu.edu/~cshalizi/rmarkdown/). Some cool things you can do:

- Inline math like $f(x) = 10$
- Inline R code like `r foo` or `r py$results$data_name`.
- Basic latex commands. For example, we'll use \\clearpage to start a page break below.

\clearpage
# Useful Code Chunks

### Code Chunks used to Setup Environment

If you open the template file using RStudio or a text editor, you will find several hidden code chunks placed before the Intro section. These code chunks are used to setup your coding environment in R, Python, and Latex. Include them at the top of every report template you create.

### Code Chunks to Create a Latex Tables with `xtable`

The [xtable package](https://cran.r-project.org/web/packages/xtable/vignettes/xtableGallery.pdf) in R lets you create Latex tables from data structures in Python and R.

Below, I show how we can use this to create a simple summary table from a Python dictionary. You should include tables like these at the top of each report to show "metadata" like, experimental parameters, the name of the results file, when the experiment was run etc.

```{python create-table-1}

info = {
    'Data Name': results['data_name'],
    'Results File': Path(r.params['report_data']).stem,
    'Report Creation Date': datetime.now().strftime("%b-%d-%Y"),
    'Rows in df': results['df'].shape[0],
    'Columns in df': results['df'].shape[1],
}

info_df = pd.DataFrame.from_records([info]).transpose()
```

```{r create-table-2, echo=TRUE, include=FALSE}

# create an xtable from a data.frame
xt = xtable(py$info_df, align = c("l", "r"))

# print the xtable as a string
n_rows = nrow(py$info_df)
xt_str = print.xtable(xt,
                      type = "latex", 
                      tabular.environment = "tabular",
                      booktabs = TRUE,
                      floating = FALSE,
                      include.rownames = TRUE,
                      include.colnames = FALSE,
                      NA.string="-",
                      comment=FALSE,
                      timestamp=FALSE,
                      hline.after=NULL,
                      add.to.row = list(pos=as.list(-1:n_rows), command=c('\\toprule ','',rep('\\midrule ',n_rows-1),'\\bottomrule\n')),
                      #
                      # use the 'sanitize' functions to process the raw data in the table
                      # use sanitize.text.function to strip special characters from latex
                      # use sanitize.rownames and sanitize.colnames to format rows and column header
                      sanitize.text.function = function(x){sanitize(x, type = "latex")},
                      sanitize.rownames.function = function(x){paste0('{\\bfseries ', x, '}')},
                      sanitize.colnames.function = function(x){paste0('{\\bfseries ', x, '}')}
                      );
```
\begin{table}[h]
\small
`r xt_str`
\end{table}

\clearpage
### Create Plot in Python using Matplotlib

```{python plt-example, fig.path = 'figure/'}
plt.plot([0, 2, 1, 4])
plt.show()
```

\clearpage
### Create Plot with `dplyr`

```{R ggplot-example, fig.path = 'figure/'}

data("midwest", package = "ggplot2");
midwest <- read.csv("http://goo.gl/G1K41K");

# create a scatterplot
gg <- ggplot(midwest, aes(x=area, y=poptotal)) +
  geom_point(aes(col=state, size=popdensity)) +
  geom_smooth(method="loess", se=F) +
  xlim(c(0, 0.1)) +
  ylim(c(0, 500000)) +
  labs(subtitle="Area Vs Population",
       y="Population",
       x="Area",
       title="Scatterplot",
       caption = "Source: midwest")

plot(gg)
```
